---
title: "Music Analysis"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r load libraries}
library(dplyr)
library(audio)
library(warbleR)
library(seewave)
```

## Play the songs
You can play songs directly from website hosting free .wav song files\f

```{r songs from site}
wav_file <- tempfile()
download.file("https://file-examples.com/wp-content/uploads/2017/11/file_example_WAV_1MG.wav", wav_file, mode = "wb")
aud_wav <- load.wave(wav_file)
audio::play(aud_wav)

```
## Visualizing the song 2D way
```{r seewave}
a <- readWave(wav_file, from = 1, to = 20, units = "seconds")
seewave::spectro(a, fastdisp = TRUE)
```
##Listen to the song
The song can be played normal, slower or faster. It opens media player window
```{r normal frequency}
# normal
listen(a,f=8000)
```
```{r faster}
# two times faster
listen(a,f=8000*2)
```
```{r slower}
# two times slower
listen(a,f=8000/2)
```
fffeffff