---
title: "Music Analysis"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r load libraries}
library(dplyr)
library(audio)
library(warbleR)
library(seewave)
```

## Play the songs

You can play songs directly from website hosting free .wav song files, for example:

```{r songs from site}
wav_file <- tempfile()
download.file("https://file-examples.com/wp-content/uploads/2017/11/file_example_WAV_1MG.wav", wav_file, mode = "wb")
aud_wav <- load.wave(wav_file)
audio::play(aud_wav)

```
Analysing the song graphically
```{r seewave}
a <- readWave(wav_file)
seewave::spectro(a, fastdisp = TRUE)
```
The sound can be played normal, slower or faster - opens media player window
```{r sound frequency}
# normal
listen(a,f=8000)
# two times faster
listen(a,f=8000*2)
# two times slower
listen(a,f=8000/2)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
